Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
adding an example for BCP.

undefined. (The placeholders library provide better keyword such as {\tt notImplemented} and {\tt todo})

>>>>

First, we write a signature and leave the definition of the function undefined.

\begin{quote}
\begin{verbatim}
rev :: [a] -> [a]
rev = undefined
\end{verbatim}
\end{quote}

\noindent Note that the placeholders library provide better keyword such as {\tt notImplemented} and {\tt todo}. Next we wrote documentation.

\begin{quote}
\begin{verbatim}
-- |
-- 'rev' @xs@ returns the elements of @xs@
-- in rev order. @xs@ must be finite.
-- 
-- >>> rev [1,2,3]
-- [3,2,1]
--
-- prop> rev [] == rev []
-- prop> rev (xs ++ ys) == rev ys ++ rev (xs::[Int])
-- prop> rev (rev xs) == (xs::[Int])

rev :: [a] -> [a]
rev = undefined
\end{verbatim}
\end{quote}

\begin{figure*}
\begin{verbatim}
  describe "rev" $ do
    it "return the first element in the last" $ property $
        \xs -> not (null xs) ==> head (rev xs) == last (xs :: [Int])

    it "return the last element in the first" $ property $
        \xs -> not (null xs) ==> last (rev xs) == head (xs :: [Int])
\end{verbatim}
\end{figure*}

\noindent We should run test in order to find errors in Haddock annotation.
Then we implement the function.

\begin{quote}
\begin{verbatim}
-- |
-- 'rev' @xs@ returns the elements of @xs@
-- in rev order. @xs@ must be finite.
-- 
-- >>> rev [1,2,3]
-- [3,2,1]
--
-- prop> rev [] == rev []
-- prop> rev (xs ++ ys) == rev ys ++ rev (xs::[Int])
-- prop> rev (rev xs) == (xs::[Int])

rev :: [a] -> [a]
rev = foldl (flip (:)) []
\end{verbatim}
\end{quote}

\noindent And test.
